\documentclass[margin,line]{res}

\usepackage[usenames,dvipsnames]{xcolor}
\usepackage[unicode=true,
            colorlinks=true,
            linkcolor=blue]{hyperref}
\hypersetup{urlcolor=BlueViolet} % Does not apply color to href's
\hypersetup{colorlinks,urlcolor=BlueViolet} % href's are correct, but navigation


\oddsidemargin -.5in
\evensidemargin -.5in
\textwidth=6.0in
\itemsep=0in
\parsep=0in

\newenvironment{list1}{
  \begin{list}{\ding{113}}{%
      \setlength{\itemsep}{0in}
      \setlength{\parsep}{0in} \setlength{\parskip}{0in}
      \setlength{\topsep}{0in} \setlength{\partopsep}{0in}
      \setlength{\leftmargin}{0.17in}}}{\end{list}}
\newenvironment{list2}{
  \begin{list}{$\bullet$}{%
      \setlength{\itemsep}{0in}
      \setlength{\parsep}{0in} \setlength{\parskip}{0in}
      \setlength{\topsep}{0in} \setlength{\partopsep}{0in}
      \setlength{\leftmargin}{0.2in}}}{\end{list}}

\pagestyle{plain} 

% -------------------------------------------------------------------------
\begin{document}
\newcommand{\link}[1]{\texttt{#1}}
\providecommand{\tightlist}{%
      \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}


\name{Erik J. Peterson\vspace*{.1in}}

\begin{resume}
\section{\sc Contact Information}
\vspace{.05in}
%=========INFO=========
\begin{tabular}{@{}p{2in}p{4in}}
{\it E-mail:}  erik.exists@gmail.com   & {\it Webpage:} \href{http://robotpuggle.com}{http://robotpuggle.com} \\
\end{tabular}


%========= RESEARCH =========
\section{\sc Research Interests}
I am a theorist who likes to take risks.

%I stubbornly reject any one research theme. 

%I love experimentalists and work that crosses disciplines.

%I work across disciplines to find places where theory and data have begun to diverge. There I use math and models to ask, \textit{what if}?


%========= WORK EXPERIENCE ==========
\section{\sc Scientific Positions}

%\vspace{-.3cm}
{\bf Carnegie Mellon University} - Pittsburgh, PA \\
{\em Research Fellow (Research Scientist)} \hfill {\bf 2018 - Present}\\
Curiosity learning. Reinforcement learning. Game theory. Cooperative AI. Astrocyte computation. Artificial neural networks. Causality (as a hobby).

%\vspace{-.3cm}
{\bf Kernel, LLC} - Los Angeles, CA\\
{\em Senior Research Scientist} \hfill {\bf 2017 - 2018}\\
Technical lead building a \emph{real-time} system for complex spatio-temporal field shaping in deep brain stimulation. Biophysical modelling. Artificial neural networks.

%\vspace{-.3cm}
{\bf U.C. San Diego} - San Diego, CA\\
{\em Postdoctoral Fellow} \hfill {\bf 2014 - 2017}\\
Novel theoretical accounts of neural oscillations. Biophysical modelling. Advised and developed machine-learning tools to analyze electrophysiological time-series data (FOOOF). Software development.

%\vspace{-.3cm}
{\bf University of Pittsburgh} - Pittsburgh, PA\\
{\em Postdoctoral Fellow} \hfill {\bf 2012 - 2013}\\
Theoretical and empirical analysis of human decision making. Machine learning analysis of fMRI data. Software development.

%\vspace{-.3cm}
{\bf Colorado State University} - Fort Collins, CO\\
{\em Graduate Research Assistant} \hfill {\bf 2006 - 2012}\\
Human reinforcement learning. Category learning. Modelling, and fMRI data analysis. Software development.

{\bf Biosearch Technologies} - Novato, CA\\
{\em Research Assistant II} \hfill {\bf 2004 - 2006}\\
Optimization of high-throughput chemistry. Reporter gene development.

{\bf Lawrence Livermore National Laboratory} - Livermore, CA\\
{\em Research Assistant} \hfill {\bf 2003 - 2004}\\
Self-assembly of virus particles to build functional nanostructures. Mechanisms of ``ink'' transfer in Dip Pen Nano-lithography.

%========= EDUCATION ==========
\section{\sc Education}
{\bf Colorado State University}, Fort Collins, CO\\
%{\em Department of Statistics}
\vspace*{-.1in}
\begin{list1}
\item[] Ph.D, Psychology \hfill {\bf 2012}
\item[] M.S., Psychology \hfill {\bf 2009}
\end{list1}

{\bf California Polytechnic State University}, San Luis Obispo, CA\\
%{\em Department of Mathematics and Statistics}
\vspace*{-.1in}
\begin{list1}
\item[] B.S., Chemistry and Biochemistry; Minor, Philosophy \hfill {\bf May 2004}
\end{list1}

%========= PUBLICATIONS ==========
\section{\sc Publications}

\input{publications.tex}


%=========== Software ================
\section{\sc Software}

\input{software.tex}

%========= TALKs ==========
\section{\sc Talks}

\input{talks.tex}

%=========== Teaching ================
\section{\sc Teaching}

\input{teaching.tex}

%=========== ACTIVITIES ================
\section{\sc Activities}

\input{activities.tex}


%=========== AWARDS ================
\section{\sc Awards}

\input{awards.tex}

%=========== Footer ================
\end{resume}
\end{document}

