Code for all projects is available as Open Source Software.

\begin{itemize}
\item
  \href{https://github.com/CoAxLab/glia_playing_atari}{glia\_playing\_atari}:
  An implementation of artificial astrocyte networks, in Python and
  PyTorch.
\item
  \href{https://github.com/CoAxLab/infomercial}{infomercial}: Simulate
  agents who seek information and reward in equal measure, in Python and
  PyTorch.
\item
  \href{https://github.com/CoAxLab/azad}{azad}: RL agents that use
  simple heuristics, in Python and PyTorch.
\item
  \href{https://github.com/voytekresearch/fakespikes}{fakespikes}: Model
  spiking as a statistical process, in Python.
\item
  \href{https://github.com/voytekresearch/pacpy}{pacpy}: Calculate
  phase-amplitude coupling in Python (and Matlab).
\item
  \href{https://github.com/voytekresearch/chinoise}{chinoise}: Create
  simple LFP simulations, with 1/f noise.
\item
  \href{https://github.com/voytekresearch/danalysis}{danalysis}: A very
  basic library for studying recurrence matrices.
\item
  \href{https://github.com/voytekresearch/pacological}{pacological}:
  Spiking simulations of good and bad PAC.
\item
  \href{https://github.com/voytekresearch/syncological}{syncological}: A
  detailed look at the synchronization and coding fidelity of gamma
  oscillations.
\item
  \href{https://github.com/voytekresearch/bw}{bw}: Toy simulations to
  try and better interpret peak bandwidth in power spectra.
\item
  \href{https://github.com/parenthetical-e/kdf}{kdf}: A language
  agnostic key-value interface for hdf5.
\item
  \href{https://github.com/parenthetical-e/rl}{rl}: A python library for
  fitting reinforcement learning models to behavioral data
\item
  \href{http://parenthetical-e.github.io/modelmodel/}{modelmodel}:
  analyze and simulate (model-based) fMRI in python
\item
  \href{https://github.com/parenthetical-e/fmrilearn}{fmrilearn}: a set
  of helper functions to analyze fMRI data in scikit-learn
\item
  \href{https://github.com/parenthetical-e/roi}{roi}: A specialized
  module for doing parametric ROI analyses of fMRI data.
\item
  \href{https://github.com/parenthetical-e/ds}{ds}: A python module for
  dynamical systems analysis. It's for learning not for real work.
\item
  \href{http://parenthetical-e.github.io/accumulate/}{accumulate}:
  Compare decision making theories baed on information accumulation
  across every possible 2 choice trial (of length L).
\item
  \href{https://github.com/parenthetical-e/bigstats}{bigstats}: A python
  library for calculating statistics, incrementally.
\item
  \href{https://github.com/parenthetical-e/similarity}{similarity}: Some
  similarity measures for perceptual categories.
\item
  \href{https://github.com/parenthetical-e/simplepsychtoolbox}{simplepsychtoolbox}:
  A set of simple functions for doing common tasks with Psychtoolbox.
\item
  \href{https://github.com/parenthetical-e/artificialGrammar}{artificialGrammar}:
  Create and analyze artificial grammars
\item
  \href{https://github.com/parenthetical-e/seq}{seq}: First, second and
  third order effects in behavioral (or other) data.
\end{itemize}
